---
title: "Summary Report"
author: "AE group5"
date: "2021/5/15"
output: html_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
fossil_fuel_combustion <- read.csv("data/fossil-fuel-primary-energy.csv",
                                   stringsAsFactors = FALSE)
```

```{r include = FALSE}
source("Script/bar_chart.R")
source("Script/pie_chart.R")
source("Script/scatter plot.R")
source("Script/aggregate_table.R")
source("Script/summary information.R")
library("knitr")
```

## Introduction

The dataset we used concerns the use of fossil fuels by country. More specifically, the data show fossil fuel consumption throughout the last few decades in a multitude of countries in terawatt-hours. The detailed data allow us to thoroughly analyze numerous trends such as the fossil fuel consumption over the years of certain countries, grouping them by either their geography or other factors. We can also compare fossil fuel consumption data to climate change data in order to have a more in-depth analysis about trends in that area and see to what extent these variables correlate.

## Summary Information

The year that had the lowest fossil fuel consumption was `r summary_info[2]` while the year that had the highest fossil fuel consumption was `r summary_info[1]`. In terms of countries in 2019, the most recent year in the data, the country with the highest fossil fuel consumption was `r summary_info[3]`. Although in terms of the entire history of the dataset, the country which used the most fossil fuels overall in absolute value terms is `r summary_info[4]`. The mean fossil fuel usage over the history of the dataset is `r summary_info[5]`.

## Aggregate Table

```{r echo=FALSE}
kable(aggregated_table)
```

The chart displays that every continent, and nearly every country, increased its fossil fuel usage from 1965 to 2019. Some notable exceptions include the United Kingdom, Sweden, Czechia, Germany, and France. Interestingly, all the countries that did decrease their fossil fuel consumption are located in Europe (although the continent of Europe as a whole increased its consumption). Another interesting insight is that China increased its consumption by more than any other individual country or continent, showing the sharp increase in its industrial capacity.

## Scatter Plot

```{r echo = FALSE}
show(scatter_plot)
```

The purpose of this scatter plot is to display the relationship between each year and the total fossil fuels consumption worldwide (in terawatt-hours). This visualization shows that there is a strong positive near linear relationship between fossil fuel usage and year, as the consumption increases nearly every year with a few outliers, namely in the late 1970s through the early 1980s and in 2009 when fuel consumption declined. Overall, the worldwide fossil fuel consumption increased by approximately 3.5 times from 1965 to 2019, and the trend is stable in it's increase showing no sign of slowing down.

## Bar Chart

```{r echo = FALSE, fig.width = 11,fig.height = 10}
show(bar_plot)
```

The purpose of this stacked bar chart is to show fossil fuel usage of each country by decade, thereby allowing to compare each individual country's usage and its increase over the years. One interesting observation is that North American virtually mirrors the usage of the United States, as that is the dominant country in the continent. China is also an interesting case due to its major increase from the prior decades. Whilst countries like the United States and the continent of Europe have three fairly equal bars, China has consumption levels that increased very dramatically. India had a similar trend to China just on a much smaller scale. What is consistent with other data visualizations is that virtually every country increased its consumption from each respective date, with only a handful of exceptions (Ex. Germany or France).


## Pie Chart

```{r echo=FALSE,fig.width = 18,fig.height = 15}
show(pie_plot)
```

The purpose of this modified pie chart is to show fossil fuel usage broken down by country in 2019, which allows to compare the relative usage of each country. As this shows the the usage in relative terms, it can be observed that China is the country that by far uses the most fossil fuels, followed by the United States (or North America and then Europe if including continents). This data visualization confirms previous information which shows China's massive increase in its fossil fuel usage, along with the stable but major level of fossil fuel consumption of the United States in recent years. It is also interesting to see how only a handful countries stand out in this plot, with the majority having fossil fuel consumption at relatively low levels comparatively.
